### 2019-05-07 papers/haskell19/1-intro.tex
Some compresUsing CompactItemize and arranged code to not break on different pages

%
% Contributions
%
The main contribution of this paper are:
%
% \vspace{-10pt}
%
\begin{itemize}
\item We identify some important limitations of performing random testing with
  automatically derived generators using state-of-the-art tools (Section
  \ref{sec:sources}).
\item We present an extensible mechanism for representing random values built
  upon different source constructions using Data Types \`a la Carte (Section
  \ref{sec:representation}).
\item We develop a modular generation schema, exploiting the composable nature
  of our representations, which are extended to encode information relevant to
  the generation process at the type level (Section \ref{sec:generators}).
\item We propose a simple type-level idiom for describing extensible generators,
  based on the types used to represent the desired shape of our random data
  (Section \ref{sec:typelevel}).\looseness=-1
\item We provide a Template Haskell tool for automatically
  deriving all the required machinery presented throughout this paper, and
  evaluate its generation performance using three real-world case studies
  (Section \ref{sec:casestudies}).
\end{itemize}

Overall, we present a novel technique for reusing automatically derived
generators in a composable fashion, in contrast with the usual paradigm of
automatically deriving ``rigid'', monolithic generators.

>>>>

%
% Contributions
%
The main contribution of this paper are:
%
%
\begin{CompactItemize}
\item We identify some important limitations of performing random testing with
  automatically derived generators using state-of-the-art tools (Section
  \ref{sec:sources}).
\item We present an extensible mechanism for representing random values built
  upon different source constructions using Data Types \`a la Carte (Section
  \ref{sec:representation}).
\item We develop a modular generation schema, exploiting the composable nature
  of our representations, which are extended to encode information relevant to
  the generation process at the type level (Section \ref{sec:generators}).
\item We propose a simple type-level idiom for describing extensible generators,
  based on the types used to represent the desired shape of our random data
  (Section \ref{sec:typelevel}).\looseness=-1
\item We provide a Template Haskell tool%
  %
  \footnote{Link will be made available for the final version of this paper.}
  %
  for automatically deriving all the required machinery presented throughout
  this paper, and evaluate its generation performance using three real-world
  case studies (Section \ref{sec:casestudies}).
\end{CompactItemize}
%
Overall, we present a novel technique for reusing automatically derived
generators in a composable fashion, in contrast with the usual paradigm of
automatically deriving ``rigid'', monolithic generators.

### 2019-05-07 papers/haskell19/2-sources.tex
Some compresUsing CompactItemize and arranged code to not break on different pages

(<+>) :: Html -> Html -> Html
(<+>) x y = Join x (Join br y)
\end{code} %$
%
These functions let us create interesting structured values representing HTML
constructions like line-breaks (|br|), bold blocks (|bold|), unordered lists
(|list|) and concatenation of values one below another (|<+>|).

>>>>

(<+>) :: Html -> Html -> Html
(<+>) x y = Join x (Join br y)
\end{code} %$
%
These functions let us encode structured HTML constructions like line-breaks
(|br|), bold blocks (|bold|), unordered lists (|list|) and concatenation of
values one below another (|<+>|).
%
\looseness=-1

### 2019-05-07 papers/haskell19/5-typelevel.tex
Some compresUsing CompactItemize and arranged code to not break on different pages

\begin{code}
type Html_Spec
  =      Con'  "Text"
  oplus  Con   "Join"         otimes 2
  oplus  Fun'  "br"           otimes 4
  oplus  Fun   "<+>"          otimes 9
  oplus  Pat   "simplify"  1  otimes 3
  oplus  Pat   "simplify"  2  otimes 5
\end{code}

>>>>

\begin{code}
type Html_Spec  =      Con'  "Text"
                oplus  Con   "Join"         otimes 2
                oplus  Fun'  "br"           otimes 4
                oplus  Fun   "<+>"          otimes 9
                oplus  Pat'  "simplify"  1  otimes 3
                oplus  Pat   "simplify"  2  otimes 5
\end{code}
